The limits of self commitment and private paternalism \thanks{}

### 2022-11-14 donde.tex
remove conflicting packages to resolve eqref issue

We maintain the stable unit treatment value assumption (SUTVA) throughout. This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. This model is too general, however, to allow us to explore the importance of paternalism. Accordingly, we impose the following standard exclusion restriction:
\begin{equation}
Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
\label{eq:exclusion}
\end{equation}
\Eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \Eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details. Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to 
\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}

\Eqref{eq:potentialOutcomes} is the key to understanding the results that follows. By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated). Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

\Eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference. In Appendix \todo{Frank: fill in}{???}, we show that
\begin{align}
\label{eq:ToTreg}
Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{ToT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
\label{eq:TuTreg}
Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TuT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
\end{align}
where the error terms $U_i$ and $V_i$ satisfy 
\[
\mathbbm{E}(V_i) = \mathbbm{E}(U_i) = \mathbbm{E}[U_i \mathbbm{1}(Z_i = z)] = \mathbbm{E}[V_i \mathbbm{1}(Z_i = z)] = 0, \quad z = 0, 1, 2.
\]
It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest. To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT. No programming is required. Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT. Again, no programming or special software is required.

>>>>

We maintain the stable unit treatment value assumption (SUTVA) throughout. This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$. This model is too general, however, to allow us to explore the importance of paternalism. Accordingly, we impose the following standard exclusion restriction:
\begin{equation}
Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
\label{eq:exclusion}
\end{equation}
\eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment. Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details. Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to 
\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
\begin{equation}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation}

\eqref{eq:potentialOutcomes} is the key to understanding the results that follows. By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated). Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. These distributions are the ingredients that we use below to explore the importance of paternalism.

@@

\eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference. In Appendix \todo{Frank: fill in}{???}, we show that
\begin{align}
\label{eq:ToTreg}
Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{ToT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
\label{eq:TuTreg}
Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TuT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
\end{align}
where the error terms $U_i$ and $V_i$ satisfy 
\[
\mathbbm{E}(V_i) = \mathbbm{E}(U_i) = \mathbbm{E}[U_i \mathbbm{1}(Z_i = z)] = \mathbbm{E}[V_i \mathbbm{1}(Z_i = z)] = 0, \quad z = 0, 1, 2.
\]
It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest. To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT. No programming is required. Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$. An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT. Again, no programming or special software is required.
